---
title: "Military Airplane Acceptance"
author: "Tyler Brown"
date: "`r Sys.Date()`"
output: html_document
---

## Import Libraries
```{r}
library(tidyr)
library(dplyr)
```

## Read the Data
```{r}
url = 'https://raw.githubusercontent.com/AlphaCurse/Military-Plane/main/militaryplaneacceptance.csv'
df = read.csv(url)
head(df)
```

## Tidy and Transform Data
Lets remove rows 2, 3 and 4 to bring the data together. Additionally, rename column 1 to Year and remove the month from the last element of that column.
```{r}
df = df %>%
  filter(!row_number() %in% c(2, 3, 4))

colnames(df)[1] = 'Year'
df$Year[7] = 1945
df
```

Converting all character columns to integers for calculations.
```{r}
df$Total = as.integer(gsub(",","",df$Total))
df$VH.Bombers = as.integer(gsub(",","",df$VH.Bombers))
df$Heavy.Bombers = as.integer(gsub(",","",df$Heavy.Bombers))
df$Medium.Bombers = as.integer(gsub(",","",df$Medium.Bombers))
df$Light.Bomber = as.integer(gsub(",","",df$Light.Bomber))
df$Fighters = as.integer(gsub(",","",df$Fighters))
df$Reconnaissance = as.integer(gsub(",","",df$Reconnaissance))
df$Transports = as.integer(gsub(",","",df$Transports))
df$Trainers = as.integer(gsub(",","",df$Trainers))
df$Communications = as.integer(gsub(",","",df$Communications))
head(df)
```

Lets replace the NA value with 0.
```{r}
df$VH.Bombers[2] = 0
df$VH.Bombers = as.integer(df$VH.Bombers)
head(df)
```

## Identify for each type of aircraft listed in the table the sharpest drop in acceptances between 2 consecutive years.
Since the analysis is of each aircraft, we can elimate the total column and grand total row.
```{r}
new_df = df %>%
  select(Year, VH.Bombers, Heavy.Bombers, Medium.Bombers, Light.Bomber, Fighters, Reconnaissance, Transports, Trainers, Communications)
head(new_df)
```
```{r}
new_df = new_df %>%
  filter(!row_number() %in% c(1))
new_df
```

For the VH Bomber airplanes, the sharpest drop was from 1943 to 1945.
```{r}
diff(new_df$VH.Bombers)
```

For the Heavy Bomber airplanes, the sharpest drop was from 1943 to 1945.
```{r}
diff(new_df$Heavy.Bombers)
```

For the Medium Bomber airplanes, the sharpest drop was from 1943 to 1945.
```{r}
diff(new_df$Medium.Bombers)
```

For the Light Bomber airplanes, the sharpest drop was from 1943 to 1945.
```{r}
diff(new_df$Light.Bomber)
```

For the Fighter airplanes, the sharpest drop was from 1943 to 1945.
```{r}
diff(new_df$Fighters)
```

For the Reconnaissance airplanes, the sharpest drop was from 1940 to 1942.
```{r}
diff(new_df$Reconnaissance)
```

For the Transport airplanes, the sharpest drop was from 1943 to 1945.
```{r}
diff(new_df$Transports)
```

For the Trainer airplanes, the sharpest drop was from 1942 to 1944.
```{r}
diff(new_df$Trainers)
```

For the Communication airplanes, the sharpest drop was from 1943 to 1945.
```{r}
diff(new_df$Communications)
```
From all of the drops, we can conclude majority of the airplanes had their sharpest drop between 1943 and 1945.